Analysis

### 2022-04-30 EDA_Chang_Noordermeer_2021.Rmd
Add CTCFBSDB processing

# Input files
fileNameIn1 <- file.path(dir_data, "data/Chang_Noordermeer_2021.xlsx")
# Output files
fileNameOut1 <- file.path(dir_data, "")
```

@@

```{r}
summary(mtx$`-log10  p-value...7`)
summary(mtx$`-log10  q-value...8`)
summary(mtx$`-log10  p-value...13`)
summary(mtx$`-log10  q-value...14`)
table(mtx$`overlap with repeat(s)`)
sum
```

@@

genome_id <- "mm10"
# Get chromosome info and match it to the chromosome order in ctcfBED
chrom_data <- GenomeInfoDb::getChromInfoFromUCSC(genome = genome_id)
chrom_data <- chrom_data[chrom_data$chrom %in% seqlevels(gr), ]
chrom_data <- chrom_data[match(seqlevels(gr), chrom_data$chrom), ]
# Check if chromosome order is the same
if (!all.equal(seqlevels(gr), chrom_data$chrom)) {
  print(paste("Chromosome order does not match for", genome_id, "genome."))
  break
}
# Assign seqinfo data
seqlengths(gr) <- chrom_data$size
isCircular(gr) <- chrom_data$circular
genome(gr)     <- genome_id

gr

# Save as RData object. subdir is the character name of the CTCF GRanges variable
fileNameOut <- "CTCF_mm10_Chang_Noordermeer_2021.RData"
save(list = gr, file = fileNameOut)
# load(file = paste0(subdir, ".RData"))

```

>>>>

# Input files
fileNameIn1 <- file.path(dir_data, "data/Chang_Noordermeer_2021.xlsx")
# download.file("https://www.biorxiv.org/content/biorxiv/early/2021/04/15/2021.04.15.440007/DC1/embed/media-1.xlsx", fileNameIn1)

# Output files
fileNameOut1 <- "results/CTCF_mm10_Chang_Noordermeer_2021.RData"
```

@@

```{r}
summary(mtx$`-log10  p-value...7`)
summary(mtx$`-log10  q-value...8`)
summary(mtx$`-log10  p-value...13`)
summary(mtx$`-log10  q-value...14`)
table(mtx$`overlap with repeat(s)`)
```

@@

genome_id <- "mm10"
# Get chromosome info and match it to the chromosome order in ctcfBED
chrom_data <- GenomeInfoDb::getChromInfoFromUCSC(genome = genome_id)
chrom_data <- chrom_data[chrom_data$chrom %in% seqlevels(gr), ]
chrom_data <- chrom_data[match(seqlevels(gr), chrom_data$chrom), ]
# Check if chromosome order is the same
if (!all.equal(seqlevels(gr), chrom_data$chrom)) {
  print(paste("Chromosome order does not match for", genome_id, "genome."))
  break
}
# Assign seqinfo data
seqlengths(gr) <- chrom_data$size
isCircular(gr) <- chrom_data$circular
genome(gr)     <- genome_id
gr

# Save as RData object.
save(list = gr, file = fileNameOut1)
# load(file = paste0(subdir, ".RData"))
```

### 2022-04-30 manuscript/manuscript.Rmd
Add CTCFBSDB processing

@@

>>>>

CTCF (CCCTC-binding factor) is a versatile transctiprion regulators that is evolutionary conserved from fruit fly to human. CTCF binds to different DNA sequences through combinatorial use of 11-zinc fingers, and shows distingc functions (transcription activation/repression and chromatin insulation).

Topologically Associating Domains (TADs) are formed via cohesin-mediated loop extrusion mechanism [@Alipour:2012aa][@Fudenberg:2016aa][@Goloborodko:2016vz][@Schwarzer:2016aa]. CTCF binding, especially in convergent orientation, has long been known to be critical for loop formation [@Dixon:2012aa].

 CTCF binding site database (CTCFBSDB), a comprehensive collection of experimentally determined and computationally predicted CTCF binding sites (CTCFBS) from the literature.

@@

CTCFBSDB assembled predictred and experimentally detected CTCF binding information. Human predictions containes 13,356 sites (hg19) and mouse predictions contained 5,504 sites (mm9).
